Blaming the Typeless: \\ Scalable, Human-Centric Python Localization

### 2018-08-24 paper/main.tex
minor fixes

To apply machine learning to analyze the data, we have to formulate the
problem into standard classification problem.
For each line of a program pair, we extracted the features mentioned in
Section \ref{sec-features}.
By performing one-hot encoding on categorical features, we can represent the
extracted features into a length $M$ feature vector $\mathbf{x} \in
\mathcal{R}^{M}$.
For the corresponding label, is represented as $1$ and $0$, which means whether
the line blamed or not.
Let the number of examples be $N$.
Given a data set $\mathcal{D} \in \{\mathbf{x}^{(i)}, y^{(i)}\}^{N}_{i=1}$,
where $\mathbf{x}^{(i)} \in \mathcal{R}^{M}$ and $y^{(i)} \in \{0, 1\}$,
a learning model will learn a function $f: \mathbf{R}^{M} \to \{0, 1\}$.
Due to the large amount of data provided in this task, we only consider the
following models which are scalable to large data set.

@@

\emph{Training methodology}
At this point we have feature vectors describing every term of every program in
our data set. The vectors from a random 30\% of the program pairs are set aside for testing and
the other 70\% are used for training.
Within the training data, we use 3-fold
cross-validation to select the best parameters for our models, before training
using those parameters on the full training set and then scoring the models
using the testing set.
Each trained model takes in any vector representing a term
in a buggy program, and returns a confidence score representing how likely it is that
that term was one of the terms changed between the fixed and buggy versions.
Thus we can treat the model as providing a \emph{ranking} over all terms by
confidence, where the top result is the one that the model deems most likely
to be changed.
For a given $k$, we score the model based on Top-$k$ accuracy: for what
proportion of the programs is a correct answer (i.e. a term that is actually
changed) present in the top $k$ results.
We retrain the models for each value of k, since a model optimized to produce
the single best result might be different from one optimized to get a good
result into the top three.

@@

In our evaluation, we used FIXME as a training set and FIXME as a held-out
evaluation set. We employed cross-validation~\cite{kohavi} to help address
the potential threat of overfitting.

@@

\emph{Ground truth.} The size of our dataset precluded the manual annotation
of each buggy program. Instead, we used historical successful
edits from actual users as our ground truth notion of the desired fault
localization. This has the advantage of aligning our algorithm with user
intuitions in cases where there are multiple logically-consistent answers
(see \secref{motex}), and thus increasing the utility of our tool. However,
this definition of ground truth may be overly permissive: the next
correct program in the historical sequence may contain additional spurious
changes beyond those strictly needed to fix the bug.
We mitigate this problem by discarding as outliers program pairs that have
changed too much. \fixme{Really? This is the first time WRW is hearing
about this. If this is true, you have to go back and mention this earlier
where we talk about ground truth definitions and data set selection.}

>>>>

To apply machine learning to analyze the data, we have to formulate the
problem into standard classification problem.
For each line of a program pair, we extracted the features mentioned in
Section \ref{sec-features}.
By performing one-hot encoding on categorical features, we can represent the
extracted features into a length $M$ feature vector $\mathbf{x} \in
\mathcal{R}^{M}$.
For the corresponding label, is represented as $1$ and $0$, which means whether
the line blamed or not.
Let the number of examples be $N$.
Given a dataset $\mathcal{D} \in \{\mathbf{x}^{(i)}, y^{(i)}\}^{N}_{i=1}$,
where $\mathbf{x}^{(i)} \in \mathcal{R}^{M}$ and $y^{(i)} \in \{0, 1\}$,
a learning model will learn a function $f: \mathbf{R}^{M} \to \{0, 1\}$.
Due to the large amount of data provided in this task, we only consider the
following models which are scalable to large dataset.

@@

\emph{Training methodology}
At this point we have feature vectors describing every term of every program in
our dataset. The vectors from a random 30\% of the program pairs are set aside for testing and
the other 70\% are used for training.
Within the training data, we use 3-fold
cross-validation to select the best parameters for our models, before training
using those parameters on the full training set and then scoring the models
using the testing set.
Each trained model takes in any vector representing a term
in a buggy program, and returns a confidence score representing how likely it is that
that term was one of the terms changed between the fixed and buggy versions.
Thus we can treat the model as providing a \emph{ranking} over all terms by
confidence, where the top result is the one that the model deems most likely
to be changed.
For a given $k$, we score the model based on Top-$k$ accuracy: for what
proportion of the programs is a correct answer (i.e. a term that is actually
changed) present in the top $k$ results.
We retrain the models for each value of k, since a model optimized to produce
the single best result might be different from one optimized to get a good
result into the top three.

@@

In our evaluation, we used 70\% as a training set and 30\% as a held-out
evaluation set. We employed cross-validation~\cite{kohavi} to help address
the potential threat of overfitting.

@@

\emph{Ground truth.} The size of our dataset precluded the manual annotation
of each buggy program. Instead, we used historical successful
edits from actual users as our ground truth notion of the desired fault
localization. This has the advantage of aligning our algorithm with user
intuitions in cases where there are multiple logically-consistent answers
(see \secref{motex}), and thus increasing the utility of our tool. However,
this definition of ground truth may be overly permissive: the next
correct program in the historical sequence may contain additional spurious
changes beyond those strictly needed to fix the bug.
We mitigate this problem by discarding as outliers program pairs that have
changed too much. \fixme{Really? This is the first time WRW is hearing
about this. If this is true, you have to go back and mention this earlier
where we talk about ground truth definitions and dataset selection.}
